\herschel\footnote{{\it Herschel} is an ESA space observatory with science instruments provided by European-led Principal Investigator consortia and with important participation from NASA.} Orion Protostar Survey (HOPS) Imaging and Photometry Results.

### 2017-04-29 HOPS/photometry/ms.tex
intro updates

\section{Introduction}
A comprehensive theory of the formation of stars, which explains the origins of stars from the local raw materials and environmental conditions, is necessary for understanding processes spanning the entire range of cosmic evolution from the formation and evolution of galaxies to the formation of planets \citep{ke2012}.  Thus, a primary goal of current Galactic star-formation research is to develop such a comprehensive narrative of star formation. However, many details and key ingredients needed to complete our picture of the star-formation process are not well understood \citep{mo07}.  In particular, one critical aspect, the connection between the raw materials and the final product (the star) is not well characterized \citep{dunham}.  In other words, while the building blocks and the conditions for the formation of stars are provided by the underlying environment, the influence of these building blocks on the subsequent population is not understood.  The importance of star-formation is further underscored by the expansive open and guaranteed-time legacy-class observing programs scheduled on major space-based observatories \spitzer\ \citep{spitzer}, and \herschel\ \footnote{In fact, the former name of \herschel, FIRST was an homage to one of primary objectives of \herschel: the study of the first stars and galaxies in their earliest stages.} \citep{herschel}.
Protostars provide useful laboratories for studying the link between the local environmental conditions and the star itself.  At the protostellar stage, the incipient star is still strongly connected with the local environment, and it is in the protostellar phase that the stellar mass is accumulated and protoplanetary disks are created \citep{c2d09}.  A detailed characterization of the protostellar evolution, thus, allows us to directly follow the evolution of raw materials into a star.
Unfortunately, this strong link to their surrounding environment also makes protostars difficult to study.  In particular:  (i) observational studies must be able to disentangle the degenerate effects of both the environment and the star-formation process itself.  And, (ii) the presence of dust in the local environment means the amount of extinction in lines-of-sight to star formation regions is abnormally high (few to several tens of magnitudes in the visual) compared to most of the rest of the Galaxy \citep{dobbs}.
To properly remove the degeneracies from (i), we require sufficient spatial resolution and multi-wavelength measurements to disentangle the emission and morphology of the various components that make up the protostar and its immediate environ.  We also require sufficiently large number of protostars in a diverse set of environmental conditions to properly investigate the role of initial conditions on the fundamental properties of the emergent star.  Further, the effects of extinction (ii, above) and the required sensitivity to detect and study a large sample of protostars is mitigated by using focusing on infrared and longer wavelengths.  The extinction at infrared and radio wavelengths is orders of magnitude lower than at optical \citep{extinction}.
Besides alleviating interstellar extinction, \spitzer\ and \herschel\ observations, in particular, confirmed long recognized views that far-IR observations of the reprocessed radiation can probe the evolution of protostars \citep{als87}.  The presence of an infalling envelope of gas and dust is the defining characteristic of a protostar. This envelope absorbs the radiation from the central accreting star+disk and reprocesses most of the luminosity into the far-IR \citep{ali}.   Far-IR observations are, therefore, absolutely crucial for efficiently identifying and studying protostars because protostars emit most of their light at those wavelengths.
The combination of the nearby Orion star-forming region and the near- to far-infrared capabilities of \herschel\ and \spitzer\ allow us to meet our main requirements (above).   Orion provides several key advantages.  \cite{orion} identified a rich sample of protostars in Orion from \spitzer\ thus providing us a collection of protostars in a variety of environmental conditions.  Star formation has been observed in a rich diversity of environments, from isolated cold globules to rich clusters. See, for example, \cite{carpenter}, \cite{feigelson}, \cite{amy2010}. At 419 pc \citep{schlafly} , Orion is relatively nearby and, thus, allows excellent spatial resolution with both \herschel\ and \spitzer.  
This paper summarizes the results from the photometry component of the \herschel\ Orion Protostar Survey (HOPS) Open Time Key Program (PI: S. T. Megeath).  This paper is one in a series describing the results from HOPS (\eg\ Stutz \etal\ 2013, Kryukova \etal\ 2014, Fischer \etal\ 2016, Furlan \etal\ 2016).  Our emphasis in this paper will be on the photometry catalog and the observed properties of protostars.  Section~\ref{sec:sample} describes our observational sample and technique.  Section~\ref{sec:dp} describes our data processing and assembly of final maps.  Section~\ref{sec:phot} discusses photometry of individual sources.  Sections~\ref{sec-results}~\&~\ref{sec:discussion} present and discuss our findings.  And, finally, our conclusions are summarized in Section~\ref{sec:conc}.

@@

>>>>

\section{Introduction}
\par
A comprehensive theory of the formation of stars, which explains the origins of stars from the local raw materials and environmental conditions, is necessary for understanding processes spanning the entire range of cosmic evolution from the formation and evolution of galaxies to the formation of planets \citep{ke2012}.  Given such far-reaching significance, a primary goal of current Galactic star-formation research has been to develop such a comprehensive narrative of star formation.  This importance is further underscored by the expansive open and guaranteed-time legacy-class observing programs scheduled on major space-based observatories \spitzer\ \citep{spitzer}, and \herschel\ \footnote{In fact, the former name of \herschel, FIRST was an homage to one of primary objectives of \herschel: the study of the first stars and galaxies in their earliest stages.} \citep{herschel}.
\par
However, many details and key ingredients  are not well understood \citep{mo07}, and are needed to complete our picture of the star formation process.  In particular, one critical aspect, the connection between the raw building blocks and the conditions for star formation provided by the underlying environment and its impact on the final product (the star) is not well characterized \citep{dunham}.
\par
Protostars provide useful laboratories for studying the link between the local environmental conditions and the star itself.  At the protostellar stage, the incipient star is still strongly connected with the local environment, and it is in the protostellar phase that the stellar mass is accumulated and protoplanetary disks are created \citep{c2d09}.  A detailed characterization of the protostellar evolution, thus, allows us to directly follow the evolution of raw materials.
\par
Unfortunately, this strong link to their surrounding environment also makes protostars difficult to study.  In particular:  (i) observational studies must be able to disentangle the degenerate effects of both the environment and the star-formation process itself.  Protostars are characterized by a central core, an accretion disk, outflows, and an infalling envelope \citep{ali}. Additionally, protostars alter their local environment with phenomenon such as Herbig-Haro objects \citep{hhobjects}.  The spatial scales for all of these components range from less than 1 AU to 100s of AUs \citep{mo07}.  Thus, observational strategies must account for this compact, yet complicated morphology.  Further, (ii) the presence of dust in the local environment means the amount of extinction in lines-of-sight to star formation regions is abnormally high (few to several tens of magnitudes in the visual) compared to most of the rest of the Galaxy \citep{dobbs}.
\par
We use a combination of strategies for {\it HOPS}\  to mitigate both challenges (i) and (ii), above.  First, we use multi-wavelength measurements to disentangle the protostar's components.  Multi-wavelength measurements are useful because they directly connect the emergent spectral properties with the underlying physical structure and conditions of said protostar component.  As these conditions vary between the components, they also vary in the emergent emission.  
\par
Second, we focus on the nearby star-forming region Orion.  Orion provides several key advantages.  \cite{orion} identified a rich sample of protostars in Orion from \spitzer\ thus providing us a collection of protostars in a variety of environmental conditions.  Star formation has been observed in a rich diversity of environments, from isolated cold globules to rich clusters. See, for example, \cite{carpenter}, \cite{feigelson}, \cite{amy2010}.   Also, at 419 pc \citep{schlafly} , Orion is relatively nearby and, thus, allows relatively high spatial resolution to resolve morphologies.

(2) Include sufficient number of protostars in a diverse set of environmental conditions, and (3)

Further, we focus on the nearby Orion star-forming region.

To properly remove the degeneracies from (i), we require sufficient spatial resolution and multi-wavelength measurements to disentangle the emission and morphology of the various components that make up the protostar and its immediate environ.  We also require sufficiently large number of protostars in a diverse set of environmental conditions to properly investigate the role of initial conditions on the fundamental properties of the emergent star.  Further, the effects of extinction (ii, above) and the required sensitivity to detect and study a large sample of protostars is mitigated by using focusing on infrared and longer wavelengths.  The extinction at infrared and radio wavelengths is orders of magnitude lower than at optical \citep{extinction}.
\par
Besides alleviating interstellar extinction, \spitzer\ and \herschel\ observations, in particular, confirmed long recognized views that far-IR observations of the reprocessed radiation can probe the evolution of protostars \citep{als87}.  The presence of an infalling envelope of gas and dust is the defining characteristic of a protostar. This envelope absorbs the radiation from the central accreting star+disk and reprocesses most of the luminosity into the far-IR \citep{ali}.   Far-IR observations are, therefore, absolutely crucial for efficiently identifying and studying protostars because protostars emit most of their light at those wavelengths.
\par
The combination of the nearby Orion star-forming region and the near- to far-infrared capabilities of \herschel\ and \spitzer\ allow us to meet our main requirements (above).   
\par
This paper summarizes the results from the photometry component of the \herschel\ Orion Protostar Survey (HOPS) Open Time Key Program (PI: S. T. Megeath).  This paper is one in a series describing the results from HOPS (\eg\ Stutz \etal\ 2013, Kryukova \etal\ 2014, Fischer \etal\ 2016, Furlan \etal\ 2016).  Our emphasis in this paper will be on the photometry catalog and the observed properties of protostars.  Section~\ref{sec:sample} describes our observational sample and technique.  Section~\ref{sec:dp} describes our data processing and assembly of final maps.  Section~\ref{sec:phot} discusses photometry of individual sources.  Sections~\ref{sec-results}~\&~\ref{sec:discussion} present and discuss our findings.  And, finally, our conclusions are summarized in Section~\ref{sec:conc}.

@@

\bibitem[]{hhobjects} O'dell, C., R., Hartigan, P., Lane, W., M., Wong, S., K., Burton, M., G., Raymond, J., \& Axon, D., 1997, AJ, 114, 730
